\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\usepackage[round]{natbib}

\title{CAS 741: Problem Statement\\Companion Cube Calculator ($C^{3}$)}

\author{Geneva Smith (\texttt{smithgm})}

\date{\today}

\input{../Comments}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 15, 2017 & Geneva Smith & Added an additional environment constraint; 
clarified the purpose of the project \\
September 14, 2017 & Geneva Smith & First draft \\
\bottomrule
\end{tabularx}
\end{table}

The GLaDOS architecture described by \citet{glados} is a specialized game 
engine that enables game designers to create Non-Player Characters (NPCs) that 
react to their environment by using models of emotion from psychology. A key 
component of the architecture is the primary appraisal module, where inputs 
from the environment are converted into emotion values. The equations currently 
used for this task are not well informed by any scientific research, and will 
be incrementally revised as more information is collected. These new equations 
are required to conform to the same mathematical range as the currently 
implemented equations. Ensuring that this requirement is maintained over 
consecutive iterations of the equations will become tedious and time consuming, 
distracting from the main task of developing more rigorous and explainable 
emotion equations. To help streamline this task, I propose the development of 
the Companion Cube Calculator ($C^{3}$).

The $C^{3}$ is a tool for calculating the range of a mathematical equation 
based on its input variables. Users will be able to specify input domains for 
variables that are known, and the tool will determine the domains for 
unspecified input variables. For example, the equation $y = x + 5$ should 
return $y \in (-\inf, \inf), x \in (-\inf, \inf)$ whereas the constrained 
equation of $y = x + 5, x \geq 0$ should return $y \in [5, \inf)$. For the 
initial version of the $C^{3}$ tool, the possible values will be limited to the 
domain of real numbers ($\Re$). In the special case of piece-wise equations, 
the ideal tool would be able to accept the full equation set as a single input. 
However, if this is beyond the scope of the initial version, piece-wise 
equations can be entered as individual equations with constrained input 
domains. This project can be implemented as a command line tool. However, one 
of the only ways to ensure that there are no user input errors is to create a 
Graphical User Interface (GUI) that will only allow syntactically correct 
inputs. If this requirement is implemented, the initial version of the $C^{3}$ 
tool will only be available for Windows operating systems.

%Computerized models of creature behaviours is a type of artificial 
%intelligence 
%(AI) that is frequently used by game designers to define  in their games. 
%While many academic approaches to AI are typically too 
%resource intensive or exact for this application, the methodical and 
%research-based approach to defining behaviour equations can be used to create 
%the desired effects. This also enables the benefits related to testing and 
%maintainability that such an approach offers. Even though this project is 
%targeted at game designers, it can be used for any project that requires the 
%development of mathematical equations.

\bibliographystyle {plainnat}
\bibliography{../../ReferenceMaterial/ProblemStatement_Refs}

\end{document}