\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{CAS 741: Problem Statement\\Companion Cube Calculator (CCC)}

\author{Geneva Smith (\texttt{smithgm})}

\date{\today}

\input{../Comments}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 14, 2017 & Geneva Smith & First draft \\
\bottomrule
\end{tabularx}
\end{table}

The Companion Cube Calculator (CCC) is a tool for calculating the range of a 
mathematical equation based on its input variables. Users will be able to 
specify input domains for variables that are known, and the tool will determine 
the domains for unspecified input variables. For example, the equation $y = x + 
5$ should return $y \in (-\inf, \inf), x \in (-\inf, \inf)$ whereas the 
constrained equation of $y = x + 5, x \geq 0$ should return $y \in 
[5, \inf)$. For the initial version of the CCC tool, the possible values will 
be limited to the domain of real numbers ($\Re$). In the special case of 
piece-wise equations, the ideal tool would be able to accept the full equation 
set as a single input. However, if this is beyond the scope of the initial 
version, piece-wise equations can be entered as individual equations with 
constrained input domains.

Computerized models of creature behaviours is a type of artificial intelligence 
(AI) that is frequently used by game designers to define Non-Player Characters 
(NPCs) in their games. While many academic approaches to AI are typically too 
resource intensive or exact for this application, the methodical and 
research-based approach to defining behaviour equations can be used to create 
the desired effects. This also enables the benefits related to testing and 
maintainability that such an approach offers. Even though this project is 
targeted at game designers, it can be used for any project that requires the 
development of mathematical equations.

\end{document}